Park run with exponential Bradley-Terry

### 2025-12-05 inst/hankin-exponential_BT.tex
work

\subsection{Theoretical results}

@@

\section{Formula 1}

@@

Again using numerical simulation, amounting to repeated evaluation of
generalised version of equations \ref{aftersim} and \ref{requalfour}
(this time with $b=10^4$ trials per point), we obtain
figure~\ref{formula1}.  From this, we see that $s$ is less than about
0.25 and $x$ is between about 0.4 and 0.8.  Recall that, in this
model, $x=0.5$ implies that the Plackett-Luce strength of each
competitor is about twice that of the next.

\begin{figure}[t]
  \begin{centering}
\includegraphics[width=4in]{formula1}  % formula1.pdf produced by exponential_BT.Rmd
\caption{Contours of log-likelihood functions \label{formula1}.  Red circle shows
  maximum likelihood estimate}
\end{centering}
\end{figure}

>>>>

\section{Theoretical results}

@@

\section{Case study: parkrun}

``Parkrun'' is a distributed community initiative that organises
weekly timed 5 km runs/walks in parks worldwide~\citep{hindley2020}.
A typical event will have 200 participants but for the purposes of
this study, we will consider only male competitors aged 55 and over, a
demographic to which the author considers himself to belong.
Table~\ref{parkruntable} shows 7 completed parkruns.  From the first
pair of numbers we see that 43 runners from our demographic attended
that particular parkrun, of whom the author placed 33.

\begin{table}[t]
  \centering
  \caption{Parkrun results}
\label{parkruntable}
\begin{tabular}{cccccccc}\\
rank   & 33 & 35 & 35 & 37 & 32 & 30 & 37\\
runners& 43 & 49 & 59 & 51 & 56 & 55 & 58
\end{tabular}
\end{table}

Using numerical simulation, in this case repeated evaluation of
equation \ref{aftersim} and a generalized version of equation
\ref{requalfour}, with $b=5\times 10^4$ trials per point, we obtain
figure~\ref{doesnotexist}.  From this, we see that $s$ is less than
about XXXXXX and $x$ is between about SXXXXASDFASDFADF and WWWWW.
SDDFDSF

Recall that, in this model, $x=0.5$ implies that the Plackett-Luce
strength of each competitor is twice that of the next; and if
$x=0.25$, we can expect

\section{Case study: Formula 1}

@@

Again using numerical simulation, amounting to repeated evaluation of
generalised version of equations \ref{aftersim} and \ref{requalfour}
(this time with $b=10^4$ trials per point), we obtain
figure~\ref{formula1}.  From this, we see that $s$ is less than about
0.25 and $x$ is between about 0.4 and 0.8.  Recall that, in this
model, $x=0.5$ implies that the Plackett-Luce strength of each
competitor is twice that of the next; and if $x=0.25$, we can expect
Hamilton to be better than a randomly chosen competitor with
probability $1-0.25=0.75$.

\begin{figure}[t]
  \begin{centering}
\includegraphics[width=4in]{formula1}  % formula1.pdf produced by exponential_BT.Rmd
\caption{Contours of log-likelihood function for Lewis Hamilton's
  Formula One performance over the 2023 season. \label{formula1} Red
  circle shows maximum likelihood estimate}
\end{centering}
\end{figure}

### 2025-12-05 inst/parkrun_idea.Rmd
another approach
work

```{r sethowmany}
howmany <- 100
```

```{r parkrunlikefunobs1, cache = TRUE}
print(system.time(parkrun01 <- single_like_fun(259, 177/259, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs2, cache = TRUE}
 print(system.time(parkrun02 <- single_like_fun(305, 222/305, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs3, cache = TRUE}
print(system.time(parkrun03 <- single_like_fun(297, 206/297, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs4, cache = TRUE}
print(system.time(parkrun04 <- single_like_fun(241, 142/241, N = howmany*10, a_try, x_try)))
```

@@

```{r parkrunlikefunobs5, cache = TRUE}
print(system.time(parkrun05 <- single_like_fun(179, 118/179, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs6, cache = TRUE}
print(system.time(parkrun06 <- single_like_fun(338, 224/338, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs7, cache = TRUE}
print(system.time(parkrun07 <- single_like_fun(203, 128/203, N = howmany, a_try, x_try)))
```

@@

```{r}
c(
sum(parkrun01),
sum(parkrun02),
sum(parkrun03),
sum(parkrun04),
sum(parkrun05),
sum(parkrun06),
sum(parkrun07)
)
```

```{r}
contour(a_try,x_try,parkrun05)
contour(a_try,x_try,parkrun06)
parkrun01*parkrun02*parkrun03*parkrun04*parkrun05*parkrun06*parkrun07
```

>>>>

```{r sethowmany}
howmany <- 1000
```

```{r parkrunlikefunobs1, cache = TRUE}
print(system.time(parkrun01 <- single_like_fun(43, 33/43, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs2, cache = TRUE}
 print(system.time(parkrun02 <- single_like_fun(49, 35/49, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs3, cache = TRUE}
print(system.time(parkrun03 <- single_like_fun(59, 35/59, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs4, cache = TRUE}
print(system.time(parkrun04 <- single_like_fun(51, 37/51, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs4, cache = TRUE}
print(system.time(parkrun05 <- single_like_fun(56, 32/56, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs4, cache = TRUE}
print(system.time(parkrun04 <- single_like_fun(55, 30/55, N = howmany, a_try, x_try)))
```

@@

```{r parkrunlikefunobs4, cache = TRUE}
print(system.time(parkrun04 <- single_like_fun(58, 37/58, N = howmany, a_try, x_try)))
```

@@

```{r}
c(
sum(parkrun01),
sum(parkrun02),
sum(parkrun03),
sum(parkrun04)
)
```

```{r}
contour(a_try,x_try,parkrun01)
contour(a_try,x_try,parkrun02)
Likelihood <-
    parkrun01*
    parkrun02*
    parkrun03*
    parkrun04*
    parkrun05*
    parkrun06*
    parkrun07
contour(a_try,x_try, Likelihood)
```

```{r}
M <- matrix(c(
259, 177,
305, 222,
297, 206,
241, 142,
179, 118,
338, 224,
203, 128),ncol=2,byrow=TRUE)
M
plot(M[,2]/M[,1])
```
